Eviction and Crime: Evidence from Boston

### 2023-04-13 writing/paper/main.tex

    Treatment effects from months 1 to 36 after treatment range from -1.54 to -4.94. The magnitudes of these point estimates are between 1.60 and 5.15 percent of the average number of crimes per month in a single property's radius in 2017

    the fact that they increase gradually during first three months after treatment is consistent with the fact that landlords have 90 days to file for execution.
    \begin{figure}[H]
        \centering
        \includegraphics{output/group_0_crimes_500m/figures/att_gt_dr_event_study_long_horizon.png}
        \caption{Relationship Between Treatment and Crime Incidents Within 500 Meters}
        \label{fig:my_label}
    \end{figure}

@@

    In this section, I argue that the most likely mechanism for the treatment effects I observe is the removal of targets of, accessories to, and/or culprits of crime incidents from the immediate vicinity of the property. Three pieces of evidence support this hypothesis.

@@

    Second, treatment effects are driven by evictions that were concluded during warm months. Post-treatment impacts of eviction are uniformly smaller in magnitude during cold months and largely insignificant from 0, as shown in Figures 4 and 5.

>>>>

    Treatment effects from months 1 to 36 after treatment range from -1.54 to -4.94. The magnitudes of these point estimates are between 1.60 and 5.15 percent of the average number of crimes per month in a single property's radius in 2017.

    \begin{figure}[H]
        \centering
        \includegraphics{output/group_0_crimes_500m/figures/att_gt_dr_event_study_long_horizon.png}
        \caption{Relationship Between Treatment and Crime Incidents Within 500 Meters}
        \label{fig:my_label}
    \end{figure}

@@

    In this section, I argue that the most likely mechanism for the treatment effects I observe is the removal of individuals who are targets of, accessories to, and/or culprits of crime incidents from the immediate vicinity of the property. Three pieces of evidence support this hypothesis.

@@

    Second, a placebo test using crimes that are more common in wealthier census tracts do not produce significant treatment effects. If the above mechanism is correct—if the effects I observe are the result of the removal of individuals who interact with crime in some capacity—then my model should estimate weaker effects of eviction on crime incidents which are less common in areas with similar poverty rates to areas where evictions are common. To implement this placebo test, I first restrict my crime dataset only to crimes which occurred between January 2019 and March 2020. For each category of crime incident in my data, I calculate the median, 75th percentile, and 99th percentile of the poverty rates of the census tracts in which that cateogry of incident occurred. I listed the ten crime incident categories with the ten lowest median census tract poverty rates. From these ten categories, I selected three: shoplifting, motor vehicle accidents, and motor vehicle towing. Table 4 gives information about the distribution of poverty rates in census tracts where these crimes occur, along with information about the distribution of poverty rates in census tracts where evictions are filed. Column 1 shows that the poverty rate of the median census tract containing a shoplifting, motor vehicle accident, or motor vehicle towing incident has a much lower poverty rate than the poverty rate of the median census tract containing an eviction filing. Similar results are shown in columns 2 and 3. Table 4 shows that shoplifting, motor vehicle accident, and motor vehicle towing incidents tend to occur in census tracts with much lower poverty rates than eviction filings.

    \begin{table}[H]
        \centering
        \input
        \caption{Caption}
        \label{tab:my_label}
    \end{table}

    Figure 5 shows that applying the doubly robust estimator from the previous section produces treatment effects that extremely small in magnitude compared to the treatment effects estimated using all crime incidents as the outcome variable. Point estimates are not uniformly positive or negative. The lack of a treatment effect of eviction on crimes which are less common in high poverty areas and which theory suggests should not be affected by eviction provides strong evidence for the mechanism I hypothesize.

    I select three categories of crime incidents which are more common in

    Second, treatment effects are driven by evictions that were concluded during warm months. Post-treatment impacts of eviction are uniformly smaller in magnitude during cold months and largely insignificant from 0, as shown in Figures 4 and 5. \textcolor{red}{todo!}

    \begin{figure}[H]
        \centering
        \includegraphics{output/group_0_crimes_warm_500m/figures/att_gt_dr_event_study_long_horizon.png}
        \caption{Relationship Between Treatment and Crime Incidents Within 500 Meters (Cases Concluded During Warm Months)}
        \label{fig:my_label}
    \end{figure}

       \begin{figure}[H]
        \centering
        \includegraphics{output/group_0_crimes_cold_500m/figures/att_gt_dr_event_study_long_horizon.png}
        \caption{Relationship Between Treatment and Crime Incidents Within 500 Meters (Cases Concluded During Cold Months)}
        \label{fig:my_label}
    \end{figure}
